The form of uncertainty affects selection for social learning

### 2022-07-04 ms.tex
finished tau sensitivity figures

\usepackage{booktabs}
\usepackage{pslatex}
\usepackage{apacite}
\usepackage{caption}
% \usepackage{subcaption}
\usepackage{wrapfig}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage{setspace}
\doublespace
% \usepackage{url}
\usepackage{bigfoot}
\usepackage[export]{adjustbox}
\setlength\intextsep{0pt}

@@

>>>>

\usepackage{booktabs}
\usepackage{pslatex}
\usepackage{apacite}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage{setspace}
\doublespace
% \usepackage{url}
\usepackage{bigfoot}
\usepackage[export]{adjustbox}
\setlength\intextsep{0pt}

@@

\newpage

\subsection{Softmax parameter sensitivity analysis}
\vspace{-3em}
\begin{figure}
  \centering
  \caption{Sensitivity analysis of the main results 
		   for the softmax parameter $\beta = 100$ and $\beta=1$. Recall the main
		   results were obtained with $\beta = 10$.}
  \label{fig:softmaxSensitivity}
  \vspace{2em}
  \begin{subfigure}{\textwidth}
	\caption{$\beta = 100$}
	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mainResultsPlots.pdf}
  \end{subfigure}
\end{figure}
\newpage
\begin{figure}
  \ContinuedFloat
  \begin{subfigure}{\textwidth}
	\caption{$\beta = 1$}
	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.pdf}
  \end{subfigure}
\end{figure}

\subsection{Number of prospective teachers sensitivty analysis}

\vspace{-3em}
\begin{figure}
  \centering
  \caption{Number of prospective teachers sensitivity analysis for $N_T=2,10,20$. Recall
  $N_T=5$ was used to generate main text results.}
  \label{fig:softmaxSensitivity}
  \vspace{2em}
  \begin{subfigure}{\textwidth}
	\caption{$N_T = 2$}
	% \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mainResultsPlots.pdf}
  \end{subfigure}
\end{figure}
\newpage
\begin{figure}
  \ContinuedFloat
  \begin{subfigure}{\textwidth}
	\caption{$N_T = 10$}
	% \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.pdf}
  \end{subfigure}
\end{figure}
\newpage
\begin{figure}
  \ContinuedFloat
  \begin{subfigure}{\textwidth}
	\caption{$N_T = 20$}
	% \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.pdf}
  \end{subfigure}
\end{figure}

\subsection{Population size sensitivty analysis}

\begin{figure}
  \centering
  \caption{
	Sensitivity analysis of the main results for different population
	sizes, $N=50,200,1000$. Recall $N=100$ was used to generate main 
	text results.
  }
  \label{fig:populationSensitivity}
  \begin{subfigure}{\textwidth}
	\caption{$N=50$}
	% \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_N=50/mainResultsPlots.pdf}
  \end{subfigure}
\end{figure}

\begin{figure}
  \ContinuedFloat
	\begin{subfigure}{\textwidth}
	  \caption{$N=200$}
	  % \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_N=200/mainResultsPlots.pdf}
	\end{subfigure}
\end{figure}

\begin{figure}
  \ContinuedFloat
	\begin{subfigure}{\textwidth}
	  \caption{$N=1000$}
	  % \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_N=1000/mainResultsPlots.pdf}
	\end{subfigure}
\end{figure}
